The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-09-05 article.tex
Rewrote picking trees with desired number of good species

The PBD model has five biological parameters, depicted in table \ref{table:parameters}, 
which we explore in a factorial fashion, excluding - for computational reasons - the combinations in which the 
95\% quantile of the expected number of good species is more than 1250.
This quantile is
calculated with the \verb;pbd_numspec_quantile; function we added to the \verb;PBD; package (\cite{pbd}).
\RAMPAL{I think we should release the new version with this function with this manuscript}
\richel{I would personally prefer 'release early, release often', but as lead maintainer you get to decide}
\RAMPAL{Do you want to put the derivation here?}
\richel{No, as you've added it to the PBD::pbd\_geom and PBD::pbd\_numspec\_quantile) documentation, so I will transfer it. Thanks!}
This calculation assumes $b = b_g = b_i$, we used $b = \max(b_g, b_i)$.
We use 1000 good species as a threshold, to prevent overly taxon-poor and taxon-rich phylogenies respectively.
The parameter values chosen are based on the parameter sets used by 
\cite{etienne2014}, as these parameters were shown to result in reasonably
sized phylogenies and using the same set allows us to compare results. 
We use a set of speciation initiation rates, $B = \{0.3, 0.5\}$, of which the speciation initiation
rate of good species $b_g \in B$ and incipient species $b_i \in B$.
\RAMPAL{your units are not entirely correct, as these are probability rates.}
\richel{I (perhaps naively) think I am correct in my units. If I am wrong, what are the correct units then? In Etienne and Rosindell 2012, there is never 'probability rate' written. To be explicit, I think theis sentence is valid: the extinction rate of good species, mu\_g has an expected 1.2 extinction events per time unit. What would be the better unit?}
\RAMPAL{Je hebt het over de eenheden van de rates. Dat is subtiel omdat het om een stochastisch model gaat en dus om kansen. Voorbeeld: mu * dt is de kans op een extinction event per species in een tijdsinterval dt. 1/mu geeft de verwachte tijd tot een extinctie event van een soort. mu is dus een probability rate.}
\richel{'mu is dus een probability rate' with what unit? You can redirect me to an article with the proper wording, or finish this sentence: 'the extinction rate of good species, mu\_g ...'. Thanks!}
The speciation completion rates we use are $\lambda = 0.1$, $0.3$, $1.0$ and $10^9$. We use $10^9 \approx \infty$
to mimic the BD model, because the PBD model reduces to the BD model for $\lambda = \infty$.
This allows us to measure the baseline error, 
which is the difference between inferred tree and true species tree that arises purely due to noise 
because the generating model and the model used in inference are identical in this case.
We use a set of extinction rates, $M = \{0.0, 0.1, 0.2, \infty\}$, of which the extinction
rate of good species $\mu_g \in M$ and incipient species $\mu_i \in M$.

From each biological parameter set, we simulate a protracted birth-death tree,
using the PBD package (\cite{pbd}) in the R programming language (\cite{r}), 
all with a crown age of 15 million years as used in \cite{etienne2014}.
Each protracted birth-death tree uses a different random number
generator seed, which makes all runs independent, resulting in a balanced 
data set.

From each incipient species tree, we construct a species tree,
by sampling one incipient/good species per good species. 
For example, when an
incipient species branched off from its mother lineage, 
both of these subspecies are recognized as representing the species, 
and hence both can be picked as an (equally good) representative of the species. 
Here, we use three sampling scenarios,
in which we pick the representative randomly or in such a way that this
results in either the shortest or longest branch lengths. 
See the supplementary information for a visualization of these sampling methods.
% \RAMPAL{Why not include that in the paper here; I think it is essential}
% \richel{Because we are limited to two figures}
Based on the sampled species tree, we simulate a DNA alignment that has the same history
as this species tree, using the \verb;phangorn; package (\cite{phangorn}). 
We set the nucleotides of the DNA alignment to follow a Jukes-Cantor (\cite{jc69})
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely. 
The DNA sequence of the root ancestor consists of four equally sized single-nucleotide blocks of adenine, cytosine, guanine and thymine respectively. 
For example, for a DNA sequence length of 12, this would be AAACCCGGGTTT. 
The order of nucletides does not matter in this study, 
because we do not consider several partitions of the sequence with their own parameters. 
Only the frequency of occurrence matters.
In our Bayesian inference (see below) we use the same site model as the (obviously correct) site model prior,
but we also explore the effect of assuming a more complex site model prior.
We predict with the more complex substitution model, 
that there will be more noise and hence our inference error will increase.
On the other hand, we dare not rule out that the inference error will decrease,
due to more flexibility in the more complex prior.
We set the mutation rate in such a way to maximize the information contained in the alignment.
To do so, we set the mutation rate such that we expect on average one (possibly silent) mutation per nucleotide
between crown age and present, which equates to $\frac{1}{15}$ mutations
per million years.
The DNA sequence length is chosen to provide a
resolution of $10^3$ years, 
% If sims take too long, we will decrease this resolution
that is, to have one expected nucleotide change 
per $10^3$ years per lineage on average. As one nucleotide is expected 
to have on average one (possibly silent) mutation per 15 million years, $15 \cdot 10^3$
nucleotides result in 1 mutation per alignment per $10^3$ years (which is
coincidentally the same as \cite{moller2018}). 
The simulation of these DNA aligments follows a strict clock model, 
which we will specify as one of the two clock models assumed in the Bayesian inference (see below).

@@

We compare each posterior phylogeny to the (sampled) species tree
using the nLTT statistic (\cite{janzen2015}), from the \verb;nLTT; package (\cite{nltt}). 
The nLTT statistic equals the area between the normalized
lineages-through-time-plots of two phylogenies, which has a range 
from zero (for identical phylogenies) to one. We use inference error 
and nLTT statistic interchangeably. Comparing the simulated species tree
with each of the posterior species trees yields a distribution of nLTT statistics.

We produce two data sets as a comma-separated file.
The general data set has 348 different combinations
of biological parameter combinations, site and clock models.
The data set to investigate sampling has 552 different combinations
of biological parameter combinations, site models, clock models 
and sampling methods. The experiment is computationally intensive:
pilot experiments show that the experiment takes roughly 100 days
of CPU time and 20 days of wall clock time (which includes the queued 
waiting for computational resources) per replicate. 
Due to this, we choose to perform ten replicates, so that the complete
experiment will take an acceptable time of roughly seven months.

For both data sets, we display the nLTT statistics distribution per
biological parameter combination as a violin plot.
We show combinations for which $b_g = b_i$ and $\mu_g = \mu_i$,
to simplify the interpretation of the results, where the other combinations
are shown in the supplementary material.
Additionally, we only show the nLTT distributions
that were generated under the (correct) assumptions of a Jukes-Cantor site model
and a strict clock model, separated per sampling method used. 
We display the nLTT statistic distributions separated per site or clock model 
in the supplementary information.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\richel{journal does not request for this. Suggest to remove, but how to acknowledge Peregrine otherwise?}
%We would like to thank the Center for Information Technology of the University of Groningen for their support
%and for providing access to the Peregrine high performance computing cluster.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Authors' contributions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\richel{journal does not request for this}
%RSE conceived the idea for this experiment. 
%RJCB created and tested the experiment, 
%and wrote the first draft of the manuscript. 
%RSE contributed substantially to revisions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description & Values \\
    \hline
    \hline
    $b_g$                 & Speciation initiation rate of a good species & 0.3, 0.5 \\
    $b_i$                 & Speciation initiation rate of an incipient species & 0.3, 0.5 \\
    $\lambda$             & Speciation completion rate & 0.1, 0.3, 1.0, $\infty$ \\
    $\mu_g$               & Extinction rate of a good species & 0.0, 0.1, 0.2 \\
    $\mu_i$               & Extinction rate of an incipient species & 0.0, 0.1, 0.2 \\
    \hline
    $t_c$                 & Crown age & 15 \\
    $\sigma_c$            & Standard deviation around crown age & 0.001 \\
    $M_s$                 & Sampling method & S, L, R \\
    $M_c$                 & Clock model & S, RLN \\
    $M_t$                 & Site model & JC69, GTR \\
    $r$                   & Mutation rate & $\frac{1}{15}$ \\
    $l_a$                 & DNA alignment length & $15K$ \\
    $f_i$                 & MCMC sampling interval & 1K or more \\
    $R_i$                 & RNG seed incipient tree and randomly sampled species tree & 1, 2, ... \\
    $R_a$                 & RNG seed alignment simulation & $R_i$ \\
    $R_b$                 & RNG seed BEAST2 & $R_i$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. Above the horizontal line is 
    the biological parameter set. 
    The RNG seed $R_i$ is 1 for the first simulation of the general data set, 2 for the next,
    and so on, up to and including 3480. The RNG seeds for the data set investigating the effect 
    of sampling continue from there, but only those RNG seeds are used in which sampling has an effect.
    The sampling methods are abbreviated as such: 'R' denotes random
    sampling, 'S' is 'shortest' and 'L' is 'longest'. Sampling method $M_s$ is random for the general
    data set. For the data set exploring the effect of sampling, we use 'shortest'
    and 'longest' for each value of $R_i$ (which are random seeds in which sampling has an effect).
    The clock models are abbreviated as 'S' for a strict and 'RLN' for a relaxed log-normal model.
    The site models are abbreviated as 'JC69' for Jukes-Cantor (\cite{jc69}) and 'GTR' for the generalized 
    time-reversible model (\cite{gtr}).
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{l l}
    \hline
    $n$ & Description \\
    \hline
    \hline
    $12$   & simulation parameters, see table \ref{table:parameters} \\
    $1000$ & nLTT statistic values \\
    $11$ & ESSes of all parameters estimated by BEAST2 (see specs below) \\
    \hline
  \end{tabular}
  \caption{
    Specification of the data sets. Each row will contain one experiment,
    where the columns contain parameters, measurements and diagnostics.
    This table displays the content of the columns. 
    $n$ denotes the number
    of columns a certain item will occupy, resulting in a table of 
    1023 columns and 20K rows.
  }
  \label{table:specs}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\richel{Start new}
The PBD model has five parameters, depicted in table \ref{table:parameters}. 
The speciation completion rates $\lambda$ we use are $0.1$, $0.3$, $1.0$ and $10^9$ probability of occurence per time unit. 
\richel{Is the unit correct unit now?}
The extinction rates $\mu = \mu_g = \mu_i$ we use are $0.0$, $0.1$ and $0.2$ probability of occurence per time unit.
We use expected mean tree sizes $n$ of 50, 100 and 200 good taxa.
From each combination of $\lambda$, $\mu$ and $n$, we derive a speciation initiation rate $b = b_i = b_g$, shown in table \ref{table:pbd_parameters}.
Our parameters are inspired on existing work \cite{etienne_and_rosindell_2012}\cite{etienne2014}.
We use $\lambda = 10^9 \approx \infty$ to let the PBD model reduce to the BD model.

We simulate protracted birth-death trees, using the PBD package (\cite{pbd}) in the R programming language (\cite{r}).
For each combination of ${\lambda, \mu, b, n}$, we generate incipient species trees with a crown age of 15 million years.
Only trees with the desired number of good taxa are kept.

This research creates two data sets: a general one, to explore parameter space, 
and one to investigate the effect of sampling incipient species (see below).
For the general data set, all the trees with the correct number of good species are kept.
For the data set to investigate sampling, only trees with the additional constraint of sampling having an effect are kept.
As sampling does not have an effect for $\lambda = \infty$, this parameter value is absent in that data set.
\richel{End new}

From each incipient species tree, we construct a species tree,
by sampling one incipient/good species per good species. 
For example, when an
incipient species branched off from its mother lineage, 
both of these subspecies are recognized as representing the species, 
and hence both can be picked as an (equally good) representative of the species. 
Here, we use three sampling scenarios,
in which we pick the representative randomly or in such a way that this
results in either the shortest or longest branch lengths.

See the supplementary information for a visualization of these sampling methods.
Based on the sampled species tree, we simulate a DNA alignment that has the same history
as this species tree, using the \verb;phangorn; package (\cite{phangorn}). 
We set the nucleotides of the DNA alignment to follow a Jukes-Cantor (\cite{jc69})
nucleotide substitution model, in which all nucleotide-to-nucleotide transitions
are equally likely. 
The DNA sequence of the root ancestor consists of four equally sized single-nucleotide blocks of adenine, cytosine, guanine and thymine respectively. 
For example, for a DNA sequence length of 12, this would be AAACCCGGGTTT. 
The order of nucletides does not matter in this study, 
because we do not consider several partitions of the sequence with their own parameters. 
Only the frequency of occurrence matters.
In our Bayesian inference (see below) we use the same site model as the (obviously correct) site model prior,
but we also explore the effect of assuming a more complex site model prior.
We predict with the more complex substitution model, 
that there will be more noise and hence our inference error will increase.
On the other hand, we dare not rule out that the inference error will decrease,
due to more flexibility in the more complex prior.
We set the mutation rate in such a way to maximize the information contained in the alignment.
To do so, we set the mutation rate such that we expect on average one (possibly silent) mutation per nucleotide
between crown age and present, which equates to $\frac{1}{15}$ mutations
per million years.
The DNA sequence length is chosen to provide a
resolution of $10^3$ years, 
% If sims take too long, we will decrease this resolution
that is, to have one expected nucleotide change 
per $10^3$ years per lineage on average. As one nucleotide is expected 
to have on average one (possibly silent) mutation per 15 million years, $15 \cdot 10^3$
nucleotides result in 1 mutation per alignment per $10^3$ years (which is
coincidentally the same as \cite{moller2018}). 
The simulation of these DNA aligments follows a strict clock model, 
which we will specify as one of the two clock models assumed in the Bayesian inference (see below).

@@

We compare each posterior phylogeny to the (sampled) species tree
using the nLTT statistic (\cite{janzen2015}), from the \verb;nLTT; package (\cite{nltt}). 
The nLTT statistic equals the area between the normalized
lineages-through-time-plots of two phylogenies, which has a range 
from zero (for identical phylogenies) to one. We use inference error 
and nLTT statistic interchangeably. Comparing the simulated species tree
with each of the posterior species trees yields a distribution of nLTT statistics. 
\richel{Start new}
The input trees generated with a $\lambda = 10^9$ allow us to measure the noise of the experiment.
For $\lambda = \infty$, the PBD model that generates the starting trees reduces to a BD model.
In the following steps, sampling will have no effect, BEAST2 will assume the correct speciation model,
and the difference between inferred tree and true species tree are explained purely due to this experimental noise.
\richel{End new}

We produce two data sets as a comma-separated file.
The general data set has 144 \richel{recalc} different combinations
of biological parameter combinations, site and clock models.
The data set to investigate sampling has ?552 \richel{recalc} different combinations
of biological parameter combinations, site models, clock models 
and sampling methods. The experiment is computationally intensive:
pilot experiments show that the experiment takes roughly 100 days
of CPU time and 20 days of wall clock time (which includes the queued 
waiting for computational resources) per replicate. 
Due to this, we choose to perform ten replicates, so that the complete
experiment will take an acceptable time of roughly seven months.

For both data sets, we display the nLTT statistics distribution per
biological parameter combination as a violin plot.
\richel{Start new}
We only show the nLTT distributions
that were generated under the (correct) assumptions of a Jukes-Cantor site model
and a strict clock model, separated per sampling method used. 
\richel{End new}
We display the nLTT statistic distributions separated per site or clock model 
in the supplementary information.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description & Values \\
    \hline
    \hline
    $b_g$                 & Speciation initiation rate of a good species & derived, see \ref{table:pbd_parameters} \\
    $b_i$                 & Speciation initiation rate of an incipient species & derived, see \ref{table:pbd_parameters} \\
    $\lambda$             & Speciation completion rate & 0.1, 0.3, 1.0, $10^9$ \\
    $\mu_g$               & Extinction rate of a good species & 0.0, 0.1, 0.2 \\
    $\mu_i$               & Extinction rate of an incipient species & 0.0, 0.1, 0.2 \\
    \hline
    $n$                   & Number of good taxa & 50, 100, 200 \\
    $t_c$                 & Crown age & 15 \\
    $\sigma_c$            & Standard deviation around crown age & 0.001 \\
    $M_s$                 & Sampling method & S, L, R \\
    $M_c$                 & Clock model & S, RLN \\
    $M_t$                 & Site model & JC69, GTR \\
    $r$                   & Mutation rate & $\frac{1}{15}$ \\
    $l_a$                 & DNA alignment length & $15K$ \\
    $f_i$                 & MCMC sampling interval & 1K or more \\
    $R_i$                 & RNG seed incipient tree and randomly sampled species tree & 1, 2, ... \\
    $R_a$                 & RNG seed alignment simulation & $R_i$ \\
    $R_b$                 & RNG seed BEAST2 & $R_i$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. Above the horizontal line is 
    the biological parameter set. 
    The RNG seed $R_i$ is 1 for the first simulation of the general data set, 2 for the next,
    and so on, up to and including 3480. The RNG seeds for the data set investigating the effect 
    of sampling continue from there, but only those RNG seeds are used in which sampling has an effect.
    The sampling methods are abbreviated as such: 'R' denotes random
    sampling, 'S' is 'shortest' and 'L' is 'longest'. Sampling method $M_s$ is random for the general
    data set. For the data set exploring the effect of sampling, we use 'shortest'
    and 'longest' for each value of $R_i$ (which are random seeds in which sampling has an effect).
    The clock models are abbreviated as 'S' for a strict and 'RLN' for a relaxed log-normal model.
    The site models are abbreviated as 'JC69' for Jukes-Cantor (\cite{jc69}) and 'GTR' for the generalized 
    time-reversible model (\cite{gtr}).
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{|l|l|l|l|l|}
    \hline
       & $\mu$ & $n$ & $\lambda$  & $b$ \\
    \hline
    1  & 0   & 50  & 0.1   & 0.30944 \\
    2  & 0.1 & 50  & 0.1   & 0.39674 \\
    3  & 0.2 & 50  & 0.1   & 0.48667 \\
    4  & 0   & 100 & 0.1   & 0.36344 \\
    5  & 0.1 & 100 & 0.1   & 0.45283 \\
    6  & 0.2 & 100 & 0.1   & 0.54425 \\
    7  & 0   & 200 & 0.1   & 0.41669 \\
    8  & 0.1 & 200 & 0.1   & 0.50759 \\
    9  & 0.2 & 200 & 0.1   & 0.6001  \\
    10 & 0   & 50  & 0.3   & 0.25717 \\
    11 & 0.1 & 50  & 0.3   & 0.34003 \\
    12 & 0.2 & 50  & 0.3   & 0.42648 \\
    13 & 0   & 100 & 0.3   & 0.30862 \\
    14 & 0.1 & 100 & 0.3   & 0.39455 \\
    15 & 0.2 & 100 & 0.3   & 0.48328 \\
    16 & 0   & 200 & 0.3   & 0.35991 \\
    17 & 0.1 & 200 & 0.3   & 0.44804 \\
    18 & 0.2 & 200 & 0.3   & 0.53841 \\
    19 & 0   & 50  & 1     & 0.2297  \\
    20 & 0.1 & 50  & 1     & 0.30759 \\
    21 & 0.2 & 50  & 1     & 0.38984 \\
    22 & 0   & 100 & 1     & 0.2778  \\
    23 & 0.1 & 100 & 1     & 0.35961 \\
    24 & 0.2 & 100 & 1     & 0.44481 \\
    25 & 0   & 200 & 1     & 0.32617 \\
    26 & 0.1 & 200 & 1     & 0.41078 \\
    27 & 0.2 & 200 & 1     & 0.49818 \\
    28 & 0   & 50  & $10^9$ & 0.21589 \\
    29 & 0.1 & 50  & $10^9$ & 0.28896 \\
    30 & 0.2 & 50  & $10^9$ & 0.36635 \\
    31 & 0   & 100 & $10^9$ & 0.26146 \\
    32 & 0.1 & 100 & $10^9$ & 0.33872 \\
    33 & 0.2 & 100 & $10^9$ & 0.41945 \\
    34 & 0   & 200 & $10^9$ & 0.30733 \\
    35 & 0.1 & 200 & $10^9$ & 0.38768 \\
    36 & 0.2 & 200 & $10^9$ & 0.47099 \\
    \hline
  \end{tabular}
  \caption{
    The speciation parameters used. Starting from extinction rate $\mu$ ($\mu = \mu_g = \mu_i$), the expected
    mean number of good species $n$, speciation completion rate $\lambda$, the speciation initation
    rate $b$ ($b = b_g = b_i$) follows.  
  }
  \label{table:pbd_parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{l l}
    \hline
    $n$ & Description \\
    \hline
    \hline
    $12$   & simulation parameters, see table \ref{table:parameters} \\
    $1000$ & nLTT statistic values \\
    $11$ & ESSes of all parameters estimated by BEAST2 (see specs below) \\
    \hline
  \end{tabular}
  \caption{
    Specification of the data sets. Each row will contain one experiment,
    where the columns contain parameters, measurements and diagnostics.
    This table displays the content of the columns. 
    $n$ denotes the number
    of columns a certain item will occupy, resulting in a table of 
    1023 \richel{recalc} columns and 20K rows.
  }
  \label{table:specs}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\richel{put this section here, as the journal does not request for this}
We would like to thank the Center for Information Technology of the University of Groningen for their support
and for providing access to the Peregrine high performance computing cluster.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Authors' contributions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\richel{put this section here, as the journal does not request for this}
RSE conceived the idea for this experiment. 
RJCB created and tested the experiment, and wrote the first draft of the manuscript. 
RSE contributed substantially to revisions.
